Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
Nope, original direction was right.
CMon.

\noindent When $F$ is contravariant, a morphism from $(I, X)$ to $(J, Y)$ is a morphism $f: I \to J$ in $D$
paired with a morphism $X \to (Ff)Y$ in $FI$. Writing $\Fam(C)$ for the Grothendieck construction
$\Grothendieck{\Set^{\op}}\Fam(-,C)$ we then have that in $\Fam(C)$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

@@

>>>>

\noindent When $F$ is contravariant, a morphism from $(I, X)$ to $(J, Y)$ is a morphism $f: I \to J$ in $D$
paired with a morphism $X \to (Ff)Y$ in $FI$. Writing $\Fam(C)$ for the Grothendieck construction
$\Grothendieck{\Set^{\op}}\Fam(-,C)$ we then have that in $\Fam(C)$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and an indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

@@

\subsection{Category of commutative monoids}

$\CMon$ is the category whose objects are the commutative monoids $M$ and morphisms $M \to M'$ are the
commutative monoid homomorphisms, with the trivial one-element monoid $\One$ as terminal object and binary
products $M \tensor M'$ given by the direct product of monoids.

\subsection{Category $\Func{\LatGal^\op}{\CMon}$}

A presheaf $F: \LatGal^\op \to \CMon$ assigns to every
bounded lattice $L$ a commutative monoid $FL$ and to every Galois connection $f: L \to L'$ .
$\Func{\LatGal^\op}{\CMon}$ is the category of presheaves of commutative monoids on $\LatGal$.
